\LARGE \bf Detection and Mitigation of Corrupted Information in Distributed Model Predictive Control Based on Resource Allocation

### 2022-07-21 article/article.tex
prevent compiling
move img folder
update copyright warning
correct error
use norm function
use RR
change copyright

@@

% \draft%
\final%
\newcommand{\id}{}
\newcommand{\price}{31.00}
\pubid{\begin{minipage}{\textwidth}\ \\[50pt]\centering
  \copyright 2021 IEEE. Personal use is permitted, but republication/redistribution requires IEEE permission.\\
See https://www.ieee.org/publications/rights/index.html for more information.
\end{minipage}}
% \makeglossaries
\markboth{Oi}{test}
\begin{document}
\maketitle
% \IEEEpeerreviewmaketitle% This command is only
% \thispagestyle{empty}
% \pagestyle{empty}

@@

\section{PRELIMINARIES AND PROBLEM STATEMENT}\label{sec:PS}
\emph{Notation:} In this paper, $\|\cdot\|$ and $\|\cdot\|_{F}$ represent the $\ell_{2}$ and Frobenius norms. $\|\vec{v}\|_{Y}$ is the weighted norm, $\|Y^{\frac{1}{2}}\vec{v}\|$.
$P_{\mathsf{T}}(\cdot)$ is the Euclidean projection onto set $\mathsf{T}$.
$\otimes$ represents the Kronecker product. $\1_{m,n}$ is a ${m\times n}$ matrix filled with $1$.
$I_{c}$ is a ${c\times c}$ identity matrix.
$\pi_{v}$ denotes the number of elements in $v$.
A vector $\vec{v}_{i}$, correspond to the $i$-th agent, and these vectors can be stacked in a vector $\vec{v}$.

@@

The $M$ subsystems are coupled under linear input constraints.
We assume as an interesting case when these constraints prevent the subsystems from meeting the systems' needs. Consequently, the constraints will always be active, yielding the same results from equality constraints~\cite{BoydVandenberghe2004}:
\begin{equation}
  \label{eq:constraint}
  \sum^{M}_{i=1}\Gamma_{i}\vec{u}_{i}(k)=\vec{u}_{\mathrm{\max}}
\end{equation}
where $\Gamma_{i}:\R^{\pi_{\vec{u}_{i}(k)}\times \pi_{\vec{u}_{i}(k)}}$ and $\vec{u}_{\mathrm{max}}:\R^{\pi_{\vec{u}_{i}(k)}\times 1}$.

@@

Delegating the iterative process of allocation update to an agent with the \emph{coordinator}'s role, we have the scheme in Fig.~\ref{fig:schemeQuantity} that illustrates the negotiation.
Observe that each block \emph{negot} solves~\eqref{eq:thetaNegot} for a respective agent $i$.
This way, the only interaction that the \emph{coordinator} has with the subsystems is via the variables $\vec{\lambda}_{i}\p$ and $\vec{\theta}_{i}\pplusone$, increasing the privacy of the subsystems.
\begin{figure}[!t]
  \centering
 \footnotesize \def\svgwidth{0.44\textwidth} \input{./img/diagQuantMod.pdf_tex}
 \caption{Scheme of DMPC using a \emph{coordinator} and $M$ agents.}\label{fig:schemeQuantity}
\end{figure}

@@

Observe in Fig.~\ref{fig:schemeSafeQuantity} that the coordinator sends $\mathring{\vec{\theta}}_{i}$ to the agents. These values may be the ones from the negotiation or other. The reason to send different values is discussed in the following subsection.
\begin{figure}[b]
  \centering
  \scriptsize \def\svgwidth{0.49\textwidth}
\input{img/diagQuantSafe2.pdf_tex}
  \caption{Scheme for Secure DMPC}\label{fig:schemeSafeQuantity}
\end{figure}

>>>>

\loop\iftrue%
\errmessage{This article is copyrighted by IEEE and should not be TeXed}%
\repeat%

@@

% \draft%
\final%
\newcommand{\id}{}
\newcommand{\price}{31.00}
\pubid{\begin{minipage}{\textwidth}\ \\[50pt]\centering
    \copyright{} 2021 IEEE.
Personal use of this material is permitted.  Permission from IEEE must be obtained for all other uses, in any current or future media, including reprinting/republishing this material for advertising or promotional purposes, creating new collective works, for resale or redistribution to servers or lists, or reuse of any copyrighted component of this work in other works.
% copyright notice in https://journals.ieeeauthorcenter.ieee.org/become-an-ieee-journal-author/publishing-ethics/guidelines-and-policies/post-publication-policies
\end{minipage}}
% \makeglossaries
\begin{document}
\maketitle
% \IEEEpeerreviewmaketitle% This command is only
% \thispagestyle{empty}
% \pagestyle{empty}

@@

\section{PRELIMINARIES AND PROBLEM STATEMENT}\label{sec:PS}
\emph{Notation:} In this paper, $\norm{\cdot}$ and $\norm{\cdot}_{F}$ represent the $\ell_{2}$ and Frobenius norms. $\norm{\vec{v}}_{Y}$ is the weighted norm, $\norm{Y^{\frac{1}{2}}\vec{v}}$.
$P_{\mathsf{T}}(\cdot)$ is the Euclidean projection onto set $\mathsf{T}$.
$\otimes$ represents the Kronecker product. $\1_{m,n}$ is a ${m\times n}$ matrix filled with $1$.
$I_{c}$ is a ${c\times c}$ identity matrix.
$\pi_{v}$ denotes the number of elements in $v$.
A vector $\vec{v}_{i}$, correspond to the $i$-th agent, and these vectors can be stacked in a vector $\vec{v}$.

@@

The $M$ subsystems are coupled under linear input constraints.
We assume as an interesting case when these constraints prevent the subsystems from meeting the systems' needs. Consequently, the constraints will always be active, yielding the same results from equality constraints~\cite{BoydVandenberghe2004}:
\begin{equation}
  \label{eq:constraint}
  \sum^{M}_{i=1}\Gamma_{i}\vec{u}_{i}(k)=\vec{u}_{\mathrm{\max}}
\end{equation}
where $\Gamma_{i}:\RR^{\pi_{\vec{u}_{i}(k)}\times \pi_{\vec{u}_{i}(k)}}$ and $\vec{u}_{\mathrm{\max}}:\RR^{\pi_{\vec{u}_{i}(k)}\times 1}$.

@@

Delegating the iterative process of allocation update to an agent with the \emph{coordinator}'s role, we have the scheme in Fig.~\ref{fig:schemeQuantity} that illustrates the negotiation.
Observe that each block \emph{negot} solves~\eqref{eq:thetaNegot} for a respective agent $i$.
This way, the only interaction that the \emph{coordinator} has with the subsystems is via the variables $\vec{\lambda}_{i}\p$ and $\vec{\theta}_{i}\pplusone$, increasing the privacy of the subsystems.
\begin{figure}[!t]
  \centering
 \footnotesize \def\svgwidth{0.44\textwidth} \input{../img/diagQuantMod.pdf_tex}
 \caption{Scheme of DMPC using a \emph{coordinator} and $M$ agents.}\label{fig:schemeQuantity}
\end{figure}

@@

Observe in Fig.~\ref{fig:schemeSafeQuantity} that the coordinator sends $\mathring{\vec{\theta}}_{i}$ to the agents. These values may be the ones from the negotiation or other. The reason to send different values is discussed in the following subsection.
\begin{figure}[b]
  \centering
  \scriptsize \def\svgwidth{0.49\textwidth}
\input{../img/diagQuantSafe2.pdf_tex}
  \caption{Scheme for Secure DMPC}\label{fig:schemeSafeQuantity}
\end{figure}
